\renewcommand{\baselinestretch}{1.5} %設定行距
\pagenumbering{roman} %設定頁數為羅馬數字
\clearpage  %設定頁數開始編譯
\sectionef
\addcontentsline{toc}{chapter}{摘~~~要} %將摘要加入目錄
\begin{center}
\LARGE\textbf{摘~~要}\\
\end{center}
\begin{flushleft}
\fontsize{14pt}{20pt}\sectionef\hspace{12pt}\quad 本學期採取個人及團體分組來學習，學習團隊合作，團體協同開發一款能在
web-based CoppeliaSim 場景中雙方或多方對玩的遊戲。
\\[12pt]

\fontsize{14pt}{20pt}\sectionef\hspace{12pt}\quad 除了設計 bubbleRob 機器人、繪製球場、設定感測器及寫程式，我覺得最重要的是學會組員間的溝通及分配工作，大家各司其職才能共同做好這份作業。\\[12pt]

\end{flushleft}
\begin{flushleft}
\fontsize{14pt}{20pt}\selectfont 此專題是利用八台 BubbleRob 雙輪車分兩組在一足球場景中進行對戰，雙
方球門分別設有感測器，雙方共有八名 BubbleRob 進行比賽。在規定時間
內，每進一球即透過程式重新從球場中線發球，但球員位置不變，並重啟賽局。模擬場景中
還須配置實體計分板顯示比賽剩餘時間與比分。在 CoppeliaSim 模擬環境中
進行測試運用上的可行性並嘗試透過埠號供使用者觀看。
\end{flushleft}
\newpage
%=--------------------Abstract----------------------=%
\renewcommand{\baselinestretch}{1.5} %設定行距
\addcontentsline{toc}{chapter}{Abstract} %將摘要加入目錄
\begin{center}
\LARGE\textbf\sectionef{Abstract}\\
\begin{flushleft}
\fontsize{14pt}{16pt}\sectionef\hspace{12pt}\quad In this semester, individuals and groups are used to study, learn teamwork, and the group collaborates to develop a
Games played against two or more parties in a web-based CoppeliaSim scenario.\\[12pt]

\fontsize{14pt}{16pt}\sectionef\hspace{12pt}\quad In addition to designing the bubbleRob robot, drawing the field, setting sensors and writing programs, I think the most important thing is to learn how to communicate and assign work among team members.\\
\end{flushleft}
\begin{flushleft}
\fontsize{14pt}{16pt}\selectfont\sectionef This topic is to use eight BubbleRob two-wheeled vehicles to divide into two groups to compete in a football scene.
There are sensors on each of the square goals, and a total of eight BubbleRobs compete on both sides. at the specified time
Inside, every time a goal is scored, the ball will be served from the center line of the court through the program, but the players' positions will remain unchanged, and the game will be restarted. simulation scene
It is also necessary to configure the physical scoreboard to display the remaining time and score of the game. In the CoppeliaSim simulation environment
Test the feasibility of the application and try to make it available for users to watch through the port number.
\end{flushleft}